Acid-induced protein gels: from gelation to stress-induced failure

### 2015-10-26 talk_Montpellier.tex
Only gdot, modeled on cas4gdl1

\begin{frame}{Microscructure: fluorescent confocal microscopy}
	\tikzsetnextfilename{structure_confocal}
	\input{fig_soundbite_palavas/structure_confocal.pgf}
	\begin{itemize}
	\item Maximum $G^\prime$ corresponds to maximum contrast between phases
	\item Characteristic size $\xi$ increases during over-acidification
	\item Casein aggregates swell $\sim$ over compressed gel $\Rightarrow$ soft glassy
	\end{itemize}
\end{frame}

\begin{frame}{Three creep regimes + softness\hfill\textsc{gdl} 4\%}
\vfill
	\tikzsetnextfilename{creep_cas4_gdl4}
	\input{fig_soundbite_palavas/creep_cas4_gdl4.pgf}
\begin{itemize}
%\item Failure scenario almost conserved: ``fibre bundle'' network
%\item Other dissipation due to softness: overcompressed gel
\item More difficult to predict failure time from fractures nucleation time
\end{itemize}

@@

\begin{frame}{Over-acidification summary}
\begin{itemize}
\item The critical network is still there but over-compressed
\item Transition to soft glassy rheology
\item Creep regimes 1 and 2 still valid but messy in the middle
\item[$\Rightarrow$] Rupture scenario of critical gel only partially valid for other gels.
\end{itemize}
\end{frame}

>>>>

\begin{frame}{Microscructure: fluorescent confocal microscopy}
	\tikzsetnextfilename{structure_confocal}
	\input{fig_soundbite_palavas/structure_confocal.pgf}
	\vspace{-1em}
	\begin{itemize}
	\item Maximum $G^\prime$ corresponds to maximum contrast between phases
	\item Pore size $\xi$ decrease during over-acidification
	\item<2> Casein aggregates swell $\sim$ over compressed gel $\Rightarrow$ soft glassy
	\end{itemize}
\end{frame}

\begin{frame}{Three creep regimes + softness\hfill\textsc{gdl} 4\%}
\vfill
	\tikzsetnextfilename{creep_cas4_gdl4}
	\input{fig_presentation/creep_cas4_gdl4.pgf}
\begin{itemize}
\item reversible, homogeneous creep $\rightarrow$ irreversible fracture growth
\item nucleation regime \alert{NOT universal}
\begin{itemize}
	\item possible to reform bond?
	\item friction between swollen strands?
	\item glassy dissipation?
\end{itemize}
\end{itemize}

@@

\begin{frame}{Over-acidification summary}
\begin{itemize}
\item The critical network is still there but over-compressed
\item Transition to soft glassy rheology
\item Power-law creep and fracture growth still present but do not rule everything
\item[$\Rightarrow$] Rupture scenario of critical gel only partially valid for other gels.
\end{itemize}
\end{frame}
